Resultados por município

### 2022-12-04 code/biclarwww/municipio_index.Rmd
lower threshold for Palmela

if (i %in% c("mafra", "sesimbra", "alcochete")){

@@

```{r minimos}
if (i %in% c("mafra", "sesimbra", "alcochete")){ 
  minimo1 = 15} else {
    minimo1 = 50 
  }

if (i %in% c("mafra", "sesimbra", "alcochete")){ 
  minimo2 = 50} else if (i %in% c("almada", "oeiras", "lisboa", "odivelas", "amadora")){
    minimo2 = 200 } else {
    minimo2 = 100
  }

>>>>

if (i %in% c("mafra", "sesimbra", "alcochete", "palmela")){

@@

```{r minimos}
if (i %in% c("mafra", "sesimbra", "alcochete", "palmela")){ 
  minimo1 = 15} else {
    minimo1 = 50 
  }

if (i %in% c("mafra", "sesimbra", "alcochete", "palmela")){ 
  minimo2 = 50} else if (i %in% c("almada", "oeiras", "lisboa", "odivelas", "amadora")){
    minimo2 = 200 } else {
    minimo2 = 100
  }
